
\lhead[\chaptername~\thechapter]{\rightmark}


\rhead[\leftmark]{}


\lfoot[\thepage]{}


\cfoot{}


\rfoot[]{\thepage}


\chapter{Quick Start}

You are about to pit your wits against a cleaver hangman in a high-definition
graphical contest of language skill! Do you have what it takes to
save lives and be the hero? Can you remain calm under pressure? If
you think you do, prove it with \mbox{Super Hangman}!


\section{TO START THE GAME:}


\subsection{For Commodore 64/128:}
\begin{enumerate}
\item Turn on your Commodore 64 or 128, disk drive and monitor.
\item After the red ``busy'' light on the disk drive goes off, insert
the \mbox{Super Hangman} disk into the disk drive with the label
side up and close the disk drive door.
\item Type: \texttt{LOAD ``{*}''.8.1} and press RETURN.
\end{enumerate}

\subsection{For Apple II:}
\begin{enumerate}
\item Insert the \mbox{Super Hangman} disk into the disk drive with the
label side up and close the disk door.
\item Turn on your Apple computer.
\end{enumerate}

\subsection{For IBM:}
\begin{enumerate}
\item Insert the \mbox{Super Hangman} disk into the disk drive.
\item Turn on your IBM PC/PCjr or clone.
\item Start the game by typing \texttt{HANGMAN}, the location of your word
file, and the number of guesses:

\begin{quote}
\texttt{A:\textbackslash{}>HANGMAN B:\textbackslash{}WORDS.DAT 8}
\end{quote}
\end{enumerate}

\section{TO QUIT THE GAME}


\subsection{For Commodore 64/128:}
\begin{enumerate}
\item Remove the \mbox{Super Hangman} disk from the drive.
\item Turn off the Commodore 64 or 128.
\item Turn off the disk drive and monitor.
\end{enumerate}

\subsection{For Apple II:}
\begin{enumerate}
\item Remove the \mbox{Super Hangman} disk from the drive.
\item Turn off the Apple computer.
\item Turn off the monitor.
\end{enumerate}

\subsection{For IBM:}
\begin{enumerate}
\item Press the \emph{CONTROL} and \emph{C} keys together.
\item Remove the \mbox{Super Hangman} disk from the drive.
\item Turn off the IBM PC/PCjr or clone.
\item Turn off the monitor.\end{enumerate}

